GHRVis:

### 2022-01-02 paper/section/related.tex
draft: related work

\section{Related Work}
\begin{table*}[!tb]
	\centering
	\resizebox{\textwidth}{!}{
		\begin{tabulary}{\textwidth}{|*{3}{l|}r|c|}
			\hhline{~|*{3}{-}|~}
			\multicolumn{1}{c|}{\textbf{Literature}} &
			\textbf{Title} &
			\textbf{Geographic Region} &
			\textbf{Number of Nodes} &
			\multicolumn{1}{c}{\textbf{Year}} \\
			\hline

@@

		\end{tabulary}
	}
	\caption{Discuss Demers cartogram}
	\label{table:challenge table}
\end{table*}

>>>>

\section{Related Work}

Cartograms combine statistical and geographical information in thematic maps. We follow the categorization of cartograms by \citeauthor{vankreveld2004Rectangular} \cite{vankreveld2004Rectangular}: contiguous, non-contiguous, rectangular, and Dorling. \citeauthor{nusrat2016State} \cite{nusrat2016State} summarize three major accuracy dimensions for cartograms: statistical, geographical, and topological. Each cartogram design may make accuracy trade-offs between dimensions, we provide an overview in Table \ref{table:accuracy}.

{
\renewcommand{\arraystretch}{1.5}
\begin{table*}[!tb]
	\centering
	\resizebox{\textwidth}{!}{
		\begin{tabulary}{\textwidth}{|*{5}{l|}}
			\hhline{~|*{3}{-}|~}
			\multicolumn{1}{c|}{} & \multicolumn{3}{c|}{\cellcolor{Mycolor2} \textbf{Accuracy}} \\
			\hhline{~|*{4}{-}}
			\multicolumn{1}{c|}{\textbf{Catogram Type}} &
			\textbf{Statistical} &
			\textbf{Geographical} &
			\textbf{Topological} &
			\textbf{Contiguity} \\
			\hline
			Contiguous & \cellcolor{Mycolor3}Varies & \cellcolor{Mycolor3}Varies & Accurate & Yes \\
			\hline
			Non-contiguous & \cellcolor{Mycolor5}\textcolor{white}{Accurate} & \cellcolor{Mycolor5}\textcolor{white}{Shape is accurate} &\cellcolor{Mycolor6}Inaccurate & No   \\
			\hline
			Rectangular & \cellcolor{Mycolor3}Varies & Shape is inaccurate & \cellcolor{Mycolor3}Varies & Yes   \\
			\hline
			Dorling & Accurate & Inaccurate & Inaccurate & No  \\
			\hline
		\end{tabulary}
	}
	\caption{\textcolor{Mycolor3}{\textbf{Trade-off between dimensions}}. \textcolor{Mycolor6}{\textbf{Dimension sacrificed}} in order to improve \textcolor{Mycolor5}{\textbf{target dimension}}'s accuracy.}
	\label{table:accuracy}
\end{table*}
}

Dorling cartograms are non-contiguous and do not preserve geography and topology. A Dorling cartogram is statistically accurate, regions are represented by circles and the statistic of interest is represented by the circle size. In Demers Cartograms, a variant of Dorling, squares are used instead to capture a certain level of topology. Dorling cartograms are unable to maintain topological accuracy as circles are often repositioned to remove overlaps. Table \ref{table:region vs node} includes a list of literature that adopts Dorling cartograms with corresponding geographical regions and node counts.

{
\renewcommand{\arraystretch}{1.5}
\begin{table*}[!tb]
	\centering
	\resizebox{\textwidth}{!}{
		\begin{tabulary}{\textwidth}{|*{3}{l|}r|c|}
			\hhline{~|*{3}{-}|~}
			\multicolumn{1}{c|}{\textbf{Literature}} &
			\textbf{Title} &
			\textbf{Geographic Region} &
			\textbf{Number of Nodes} &
			\multicolumn{1}{c}{\textbf{Year}} \\
			\hline

@@

		\end{tabulary}
	}
	\caption{}
	\label{table:region vs node}
\end{table*}
}

Rectangular cartograms are contiguous and do not preserve geographical accuracy. Depending on the variant, a rectangular cartogram may trade between statistical and topological accuracy.

Mosaic cartograms are contiguous and sacrifice statistical accuracy to preserve some level of geographical accuracy. Some variants are able to preserve topological accuracy as well.
